Benchmarking the accelerated oblique random survival forest

### 2022-05-09 index.Rmd
prepping for tar_future with 1 core

data_tbl <- bm_pred_comb |> 
  mutate(model = recode(model, 'cif' = 'party')) |> 
  group_by(model, data) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |> 
  bind_rows(results_overall) |> 
  group_by(data) |> 
  mutate(
    across(.cols = starts_with("time"), .fns = as.numeric),
    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf'],
    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf']
  ) |> 
  transmute(
    model, 
    data = recode(
      data,
      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
      'sim' = 'Simulated data'
    ),
    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
    time_fit_mean = format(round(time_fit_mean, 4), nsmall = 4),
    time_fit_ratio = table_value(time_fit_ratio),
    time_prd_mean = format(round(time_prd_mean, 4), nsmall = 4),
    time_prd_ratio = table_value(time_prd_ratio)
  )

@@

data_gt <- bm_vi_comb |>
  group_by(n_obs, xcorr, model) |> 
  summarize(
    across(
      .cols = c(overall, x, w, g, v),
      .fns = function(x) table_glue("{mean(x)}")
    )
  ) |> 
  ungroup() |> 
  mutate(
    xcorr = recode(
      xcorr, 
      '0.0' = '|Corr(linear effect variables, irrelevant variables)| = 0',
      '0.1' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.10',
      '0.2' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.20',
      '0.3' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.30',
      '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'),
    model = factor(
      model,
      levels = c('aorsf',
                 'aorsf_menze',
                 'xgboost',
                 'randomForestSRC',
                 'ranger'),
      labels = c('Negation importance',
                 'ANOVA importance',
                 'SHAP importance',
                 'Permutation importance (SRC)',
                 'Permutation importance (ranger)')
    )
  ) |> 
  select(model, overall, x, w, g, v) |> 
  arrange(model)

>>>>

data_tbl <- bm_pred_comb |> 
  mutate(model = recode(model, 'cif' = 'party')) |> 
  group_by(model, data, n_z, n_obs, correlated_x) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |> 
  bind_rows(results_overall) |> 
  mutate(
    data = if_else(
      is.na(n_z),
      true = data,
      false = as.character(
        glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr \u2264 {correlated_x}")
      )
    )
  ) |> 
  group_by(data) |> 
  mutate(
    across(.cols = starts_with("time"), .fns = as.numeric),
    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf-1'],
    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf-1']
  ) |> 
  arrange(data, desc(cstat_mean)) |> 
  transmute(
    model, 
    data = recode(
      data,
      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
      'sim' = 'Simulated data'
    ),
    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
    time_fit_mean = format(round(time_fit_mean, 4), nsmall = 4),
    time_fit_ratio = table_value(time_fit_ratio),
    time_prd_mean = format(round(time_prd_mean, 4), nsmall = 4),
    time_prd_ratio = table_value(time_prd_ratio)
  )

@@

data_gt <- bm_vi_comb |>
  group_by(n_obs, xcorr, model) |> 
  summarize(
    across(
      .cols = c(overall, x, w, g, v),
      .fns = function(x) table_glue("{mean(x)}")
    )
  ) |> 
  ungroup() |> 
  mutate(
    xcorr = recode(
      xcorr, 
      '0.0' = '|Corr(linear effect variables, irrelevant variables)| = 0',
      '0.1' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.10',
      '0.2' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.20',
      '0.3' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.30',
      '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'
    ),
    model = factor(
      model,
      levels = c('aorsf',
                 'aorsf_menze',
                 'xgboost',
                 'randomForestSRC',
                 'ranger'),
      labels = c('Negation importance',
                 'ANOVA importance',
                 'SHAP importance',
                 'Permutation importance (SRC)',
                 'Permutation importance (ranger)')
    )
  ) |> 
  select(model, xcorr, overall, x, w, g, v) |> 
  arrange(model)
